---
title: "Examples"
author: "John Coene"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Examples}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(nethoser)
```

## Data

This vignette uses a dataset of 272 news and blog articles about the R programming language but you can collect your own data using the [webhoser](https://webhoser.john-coene.com/) package which is an R wrapper to the [webhoser.io](https://webhose.io/) API.

```{r}
library(webhoser)

data("webhoser")
```

## Basics

The package only consists of one dataset and two functions:

1. `connect` to build a graph by _connecting_ variables.
2. `visualise` a convenience function which uses [sigmajs](http://sigmajs.john-coene.com/) to visualise the graph.

The `connect` function returns a list of nodes and edges.

```{r}
g <- webhoser %>% 
    connect(entities.locations)

class(g)
```

You can unpack the graph with the `%<-%` assignment exported from the `zeallot` package.

```{r}
c(nodes, edges) %<-% g
```

## Co-mentions

We can build graphs of co-mentions by only passing one variable to the `connect` function.

```{r}
webhoser %>% 
    connect(entities.persons) %>% 
    visualise()
```

# Graph

```{r}
webhoser  %>% 
    connect(
        thread.site,
        entities.persons
    ) %>% 
    visualise()
```

